### 2021-04-14 priority-gv.tex
Minor changes.

\begin{compacttheorems}
  \begin{definition}[Canonical Forms]%
    \label{def:pgv-canonical-forms}
    A~configuration $\tm{\conf{C}}$ is in canonical form if it is of the form
    \(
    \tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;N)}}}
    \)
    where no term $\tm{M_i}$ is a value.
  \end{definition}
  \begin{restatablelemma}{lempgvcanonicalforms}[Canonical Forms]%
    \label{lem:pgv-canonical-forms}
    If $\cseq[\main]{\ty{\Gamma}}{\conf{C}}$, there exists some $\tm{\conf{D}}$ such that $\tm{\conf{C}}\equiv\tm{\conf{D}}$ and $\tm{\conf{D}}$ is in canonical form.
  \end{restatablelemma}
  \begin{definition}[Normal Forms]%
    A~configuration $\tm{\conf{C}}$ is in normal form if it is of the form
    \(
    \tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;V)}}}
    \)
    where each $\tm{M_i}$ is ready to act on $\tm{x_i}$.
  \end{definition}
  \begin{restatabletheorem}{thmpgvclosedprogressconfs}[Progress, $\cred$]%
    \label{thm:pgv-closed-progress-confs}
    If $\cseq[\main]{\emptyenv}{\conf{C}}$ and $\tm{\conf{C}}$ is in canonical form, then either $\tm{\conf{C}}\cred\tm{\conf{D}}$ for some $\tm{\conf{D}}$; or $\tm{\conf{C}\equiv\conf{D}}$ for some $\tm{\conf{D}}$ in normal form.
  \end{restatabletheorem}
  \begin{proof}[Sketch]
    Our proof follows the reasoning by Kobayashi~\cite{kobayashi06} used in the proof of deadlock freedom for closed processes (Theorem 2). We apply \cref{lem:pgv-open-progress-terms} to each thread. Either we obtain a reduction, or each child thread is ready and the main thread ready or a value. We pick the ready term $\tm{L}$ with the smallest priority bound. If $\tm{L}$ contains new, spawn, or a link, we apply \LabTirName{E-New}, \LabTirName{E-Spawn}, or \LabTirName{E-Link}. Otherwise, $\tm{L}$ must be ready on some $\tm{x_i}$. Linearity guarantees there is some thread  $\tm{L'}$ which acts on $\tm{x'_i}$. If $\tm{L'}$ is ready, priority typing guarantees it is ready on $\tm{x'_i}$, and we apply \LabTirName{E-Send} or \LabTirName{E-Close}. If $\tm{L'}$ is not ready, it must be the main thread returning a value. We move $\tm{L}$ into the $i^{\text{th}}$ position and repeat until we either find a reduction or reach normal form.
  \end{proof}
  \begin{corollary}%
    \label{cor:pgv-closed-progress}
    If $\cseq[\main]{\emptyenv}{\conf{C}}$, $\tm{\conf{C}}\centernot\cred$, and $\tm{\conf{C}}$ contains no endpoints, then $\tm{\conf{C}}\equiv\tm{\phi\;V}$ for some value $\tm{V}$.
  \end{corollary}
\end{compacttheorems}
It follows immediately from \cref{thm:pgv-closed-progress-confs} and \cref{cor:pgv-closed-progress} that a term which does not return an endpoint will complete all its communication actions, thus satisfying deadlock freedom.
\end{document}

>>>>

\begin{compacttheorems}
  \begin{definition}[Canonical Forms]%
    \label{def:pgv-canonical-forms}
    A~configuration $\tm{\conf{C}}$ is in canonical form if it is of the form
    \(
    \tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;N)}}}
    \)
    where no term $\tm{M_i}$ is a value.
  \end{definition}
  \begin{restatablelemma}{lempgvcanonicalforms}[Canonical Forms]%
    \label{lem:pgv-canonical-forms}
    If $\cseq[\main]{\ty{\Gamma}}{\conf{C}}$, there exists some $\tm{\conf{D}}$ such that $\tm{\conf{C}}\equiv\tm{\conf{D}}$ and $\tm{\conf{D}}$ is in canonical form.
  \end{restatablelemma}
  \begin{definition}[Normal Forms]%
    A~configuration $\tm{\conf{C}}$ is in normal form if it is of the form
    \(
    \tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(\child\;M_1\parallel\dots\parallel\child\;M_m\parallel\main\;V)}}}
    \)
    where each $\tm{M_i}$ is ready to act on $\tm{x_i}$.
  \end{definition}
  \begin{restatabletheorem}{thmpgvclosedprogressconfs}[Progress, $\cred$]%
    \label{thm:pgv-closed-progress-confs}
    If $\cseq[\main]{\emptyenv}{\conf{C}}$ and $\tm{\conf{C}}$ is in canonical form, then either $\tm{\conf{C}}\cred\tm{\conf{D}}$ for some $\tm{\conf{D}}$; or $\tm{\conf{C}\equiv\conf{D}}$ for some $\tm{\conf{D}}$ in normal form.
  \end{restatabletheorem}
  \begin{proof}[Sketch]
    Our proof follows that of Kobayashi~\cite[theorem 2]{kobayashi06}. We apply \cref{lem:pgv-open-progress-terms} to each thread. Either we obtain a reduction, or each child thread is ready and the main thread ready or a value. We pick the ready term $\tm{L}$ with the smallest priority bound. If $\tm{L}$ contains new, spawn, or a link, we apply \LabTirName{E-New}, \LabTirName{E-Spawn}, or \LabTirName{E-Link}. Otherwise, $\tm{L}$ must be ready on some $\tm{x_i}$. Linearity guarantees there is some thread  $\tm{L'}$ which acts on $\tm{x'_i}$. If $\tm{L'}$ is ready, priority typing guarantees it is ready on $\tm{x'_i}$, and we apply \LabTirName{E-Send} or \LabTirName{E-Close}. If $\tm{L'}$ is not ready, it must be the main thread returning a value. We move $\tm{L}$ into the $i^{\text{th}}$ position and repeat until we either find a reduction or reach normal form.
  \end{proof}
  \begin{corollary}%
    \label{cor:pgv-closed-progress}
    If $\cseq[\phi]{\emptyenv}{\conf{C}}$, $\tm{\conf{C}}\centernot\cred$, and $\tm{\conf{C}}$ contains no endpoints, then $\tm{\conf{C}}\equiv\tm{\phi\;V}$ for some value $\tm{V}$.
  \end{corollary}
\end{compacttheorems}
It follows immediately from \cref{thm:pgv-closed-progress-confs} and \cref{cor:pgv-closed-progress} that a term which does not return an endpoint will complete all its communication actions, thus satisfying deadlock freedom.
\end{document}
